### 2014-12-17 highdim-paper/paper.tex
paper outline

%
% File acl2014.tex
%
% Contact: koller@ling.uni-potsdam.de, yusuke@nii.ac.jp
%%
%% Based on the style files for ACL-2013, which were, in turn,
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt]{article}
\usepackage{acl2014}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}

%\setlength\titlebox{5cm}

% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\title{High-Dim Project}

\author{name1 \\
  Columbia University\\
  {\small \tt uni1@columbia.edu} \\\And
  name2 \\
  Columbia University\\
  {\small \tt uni2@columbia.edu} \\\And
  name3\\
  Columbia University\\
  {\small \tt uni3@columbia.edu} \\}
\date{}

\begin{document}
\maketitle
%\begin{abstract}
%  This document contains the instructions for preparing a camera-ready
%  manuscript for the proceedings of ACL-2014. The document itself
%  conforms to its own specifications, and is therefore an example of
%  what your manuscript should look like. These instructions should be
%  used for both papers submitted for review and for final versions of
%  accepted papers.  Authors are asked to conform to all the directions
%  reported in this document.
%\end{abstract}

\section{Introduction}

\section{Background}

\subsection{Latent Group Lasso}

\subsection{Multiclass Classification with Group Lasso}

\section{Our Model}

\section{Data}

\subsection{Newsgroup Data}

\subsubsection{Group Identification}

\subsection{artificial data}

\section{Results}

\section{Conclusion}
% include your own bib file like this:
%\bibliographystyle{acl}
%\bibliography{acl2014}

%\begin{thebibliography}{}
%
%\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
%Alfred~V. Aho and Jeffrey~D. Ullman.
%\newblock 1972.
%\newblock {\em The Theory of Parsing, Translation and Compiling}, volume~1.
%\newblock Prentice-{Hall}, Englewood Cliffs, NJ.
%
%\bibitem[\protect\citename{{American Psychological Association}}1983]{APA:83}
%{American Psychological Association}.
%\newblock 1983.
%\newblock {\em Publications Manual}.
%\newblock American Psychological Association, Washington, DC.
%
%\bibitem[\protect\citename{{Association for Computing Machinery}}1983]{ACM:83}
%{Association for Computing Machinery}.
%\newblock 1983.
%\newblock {\em Computing Reviews}, 24(11):503--512.
%
%\bibitem[\protect\citename{Chandra \bgroup et al.\egroup }1981]{Chandra:81}
%Ashok~K. Chandra, Dexter~C. Kozen, and Larry~J. Stockmeyer.
%\newblock 1981.
%\newblock Alternation.
%\newblock {\em Journal of the Association for Computing Machinery},
%  28(1):114--133.
%
%\bibitem[\protect\citename{Gusfield}1997]{Gusfield:97}
%Dan Gusfield.
%\newblock 1997.
%\newblock {\em Algorithms on Strings, Trees and Sequences}.
%\newblock Cambridge University Press, Cambridge, UK.
%
%\end{thebibliography}

\end{document}

### 2014-12-17 highdim-paper/paper.tex
updated 4.2

@@
 \usepackage{latexsym}
+\usepackage{graphicx}
+
+\DeclareGraphicsExtensions{.pdf,.png,.jpg}
 
@@
 
-\subsection{artificial data}
+\subsection{Artificial data}
+
+For the datasets described above, we can't tell with 100 percent confidence that the datasets follow the assumptions of the group structures for the features.
+And even if they are indeed structured that way, we maybe wrong with the method of coming up with the groups.
+These issues make it difficult to access our model.\\
+
+To get rid of all these problems and validate the effectiveness of our model, we created artificial data that followed the underlying assumptions of the model.
+First, we generate a sparse weight matrix M to represent the relationship between features and classes.
+The weight matrix M has an internal structure in which features are grouped together.
+And also, only a small number of groups have non-zero weights.
+This makes the matrix sparse.\\
+
+\begin{figure}[ht]
+\begin{center}
+	\includegraphics[natwidth=200, natheight=306]{m_img}
+	\caption{Group-wise sparse weight matrix generated: 6 classes, 30 features in 5 groups}
+\end{center}
+\end{figure}
+
+Then we generate random vectors, each of which has the length of the number of all features, and calculate dot product with the weight matrix M to get the class assignments for these random vectors.
+The random vetors X and the class assignments Y make up the training data set.
+\\
+
+Our goal is to infer this weight matrix M from X and Y using our model.
+By generating the data set using this method, we can test the effectiveness of our model on a noiseless dataset with right underlying assumptions.\\
 

### 2014-12-17 highdim-paper/gen_pdf.sh

@@ -1,0 +1,2 @@
+latex paper.tex && dvipdfm paper.dvi
+

### 2014-12-17 newimplgroup_syn.py
less verbose

@@ -77,19 +77,18 @@ def fit(ds, y, one_over_n, n_samples, n_features, n_classes,coefs_,groups):
                     Lblock=max(Lblock,hj[m])
                 Lblock = min(Lblock, 1e9)
                 Vblock=coefs_[group[0]:group[1],m] - Gblock/Lblock
-                print Vblock
+                #print Vblock
                 muj = lamb/Lblock
-                print muj
+                #print muj
                 L2 = np.linalg.norm(Vblock,2)
                 if L2 !=0 :
                     Wblock=max(1- muj/ np.linalg.norm(Vblock,2),0)*Vblock
                 else:
                     Wblock=np.zeros(group[1]-group[0])
                 loss = calculate_loss(ds,y, n_samples,n_features, n_classes,coefs_,lamb,groups)
-                print "loss: ", loss
                 Wblock_old = coefs_[group[0]:group[1],m].copy()
                 delta = Wblock - Wblock_old
-                print "delta", delta
+                #print "delta", delta
                 max_loop = 10
                 alpha = 0.5
                 alphas = 1
@@ -99,13 +98,14 @@ def fit(ds, y, one_over_n, n_samples, n_features, n_classes,coefs_,groups):
                     newLoss = calculate_loss(ds,y, n_samples,n_features, n_classes,coefs_,lamb, groups)
                     #print "new coefs", coefs_,"new loss", newLoss
                     if newLoss < loss:
-                        print "better",group[0],m
+                        print "loss: ", loss
+                        #print "better",group[0],m
                         break
                     alphas *= alpha
                     max_loop -= 1
                 if max_loop ==0:
                     coefs_[group[0]:group[1],m] = Wblock_old
-                print coefs_
+    print coefs_
 
 def score(X, y, coefs_):
     pred = safe_sparse_dot(X, coefs_)
@@ -118,12 +118,12 @@ def score(X, y, coefs_):
 
 np.set_printoptions(precision=3)
 
-m_classes = 6
-m_features = 30
-m_groups = 4
+m_classes = 5
+m_features = 25
+m_groups = 5
 m_no_in_each_group = m_features/m_groups
 multiple = 1.3
-m_samples = 60
+m_samples = 150
 attemp = 0
 
 while 1:
@@ -173,4 +173,26 @@ ds = ColumnData(X)
 coefs_ = np.zeros((n_features, n_classes))
 
 fit( ds, y, one_over_n, n_samples, n_features, n_classes,coefs_,groups)
[…]

### 2014-12-17 ogroup_test_syn.py

@@ -21,6 +21,8 @@ multiple = 1.3
 m_samples = 300
 attemp = 0
 
+np.set_printoptions(precision=4)
+
 while 1:
     attemp +=1
     print 'attemp', attemp
@@ -59,10 +61,10 @@ y_train = y_pred
 print "### BASELINE GROUP LASSO in pure python/numpy###"
 X = X_train
 y = y_train
-clf = ogroup.BaselineGroupLasso(max_iter=30, alpha=.5, max_steps=30)
+clf = ogroup.BaselineGroupLasso(max_iter=30, alpha=.8, max_steps=30)
 clf.fit(X, y, groups)
 print "Acc:", clf.score(X, y)
-print clf.coefs_
+print (clf.coefs_)
 
 
 print "### Equivalent Lightning Cython Implementation ###"
@@ -77,21 +79,5 @@ light_clf = CDClassifier(penalty="l1/l2",
                          verbose=3,
                          random_state=0).fit(X, y)
 print "Acc:", light_clf.score(X, y)
-print light_clf.coef_.T
+print (light_clf.coef_.T)
 
-
-exit(0)
-
-import numpy as np
-data = np.load('3ng_train.npz')
-X = data['X'].item()
-Xaug = data['Xaug'].item()
-y = data['y']
-groups = data['groups']
-clf.fit(Xaug, y, groups)
-print clf.score(Xaug, y)
-
-light_clf.verbose=1
-light_clf.fit(X, y)
-
-print light_clf.score(X, y)

### 2014-12-17 highdim-paper/paper.tex
Added a little bit in 'Our model' section.

@@
 
+Given n training vectors $x_i \in R_d$ and their class labels $y_i \in \{1, ..., m\}$, our goal is to compute $W$ such that it maximizes the accurarcy of our prediction and it is group-wise sparse. \\
+
+In our model, we minimize the following objective function : \\
+
+$minimize_{W \in R^{d x m}} F(W) = $
+
+$\frac{1}{n} \sum_{i=1}^{n} \sum_{r \neq y_i } max(1 - W_{:y_i} \cdot x_i + W_{:r} \cdot x_i , 0 )^2 $
+
+$ + \lambda \sum_{g=1}^{|G|} \sum_{m=1}^{d} \| W_{g,m} \|_2$ \\
+
+The first term is the multiclass squared hinge loss function.
+We want the dot product of an instance and its feature vector to be as large as possible, and the dot product of this instance and the rest feature vectors to be as small as possible.
+And as long as their difference is greater then a margin ($1$ in this case), we won't penalize it.
+In the second term, $W_{g,m}$ means a block of weights in group $g$ and class $m$.
+The L2 norm regulization is computed and sum up for each block.
+The $\lambda > 0$ is a parameter controls the trade-off between the hinge loss and the L2-norm regulization.
+\\
+
 \section{Data}
@@
 To get rid of all these problems and validate the effectiveness of our model, we created artificial data that followed the underlying assumptions of the model.
-First, we generate a sparse weight matrix M to represent the relationship between features and classes.
-The weight matrix M has an internal structure in which features are grouped together.
+First, we generate a sparse weight matrix W to represent the relationship between features and classes.
+The weight matrix W has an internal structure in which features are grouped together.
 And also, only a small number of groups have non-zero weights.
@@
 
-Then we generate random vectors, each of which has the length of the number of all features, and calculate dot product with the weight matrix M to get the class assignments for these random vectors.
+Then we generate random vectors, each of which has the length of the number of all features, and calculate dot product with the weight matrix W to get the class assignments for these random vectors.
 The random vetors X and the class assignments Y make up the training data set.
@@
 
-Our goal is to infer this weight matrix M from X and Y using our model.
+Our goal is to infer this weight matrix W from X and Y using our model.
 By generating the data set using this method, we can test the effectiveness of our model on a noiseless dataset with right underlying assumptions.\\

### 2014-12-17 newimplgroup_syn.py

@@ -176,6 +176,8 @@ fit( ds, y, one_over_n, n_samples, n_features, n_classes,coefs_,groups)
 s =  score (X,y,coefs_)
 print "score = ", s
 
+print '======================================================'
+
 clf_max_iter=300
 clf_tol = 1e-3
 print "### Equivalent Lightning Cython Implementation ###"

### 2014-12-18 highdim-paper/paper.tex
Added 2.1 and 2.2

@@
 \usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage[]{algorithm2e}
 
@@
 
+\subsection{Multiclass Classification with Group Lasso}
+
+The task of multiclass classification involves the prediction of a class label
+$l$ where the number of possible labels is $k>2$. More often than not, the 
+original problem is transformed into $k$ binary classification problems, i.e.
+$1$--vs.--all classification and positive prediction with the highest 
+confidence is selected as the label. This approach has the disadvantage of
+having to train $k$ different models.
+
+An alternative formulation, direct multiclass classification, tackles this 
+problem directly by solving the following $\operatorname{argmax}$ problem:
+$$y_i = \operatorname{argmax}_c W_{:c}^T x_i $$
+where $W \in \mathcal{R}^{p \times k}$ is a weight matrix, with $W_{ij}$
+corresponding to the $i$-th feature of class $j$. In this paper, we refer
+to features as elements in the instance data $x$. A feature in $x$ is
+associated with $k$ weights in $W$, one for each class.
+
+The decision function above suggests a max-margin style loss function. More
+specifically, we use the squared hinge loss:
+
+$$ l(W) = \sum_{i=1}^n \sum_{r\ne y_i}^k 
+    \max\left(1 - (W_{:y_i}^Tx_i - W_{:r}^Tx_i), 0\right)^2 $$
+
+The minimization of $l$ directly will lead to a minimizer $W^*$ that is
+dense. Sparse solutions are often explicitly sought, with model compactness
+leading to fast prediction at test time. In order to obtain a sparse $W^*$,
+a regularization term $r(W)$ is often applied, yielding the objective 
+function:
+
+$$\min_W l(W) + r(W).$$
+
+Many choices are available for the regularizer $r$. In (ref ???), they use
+the group lasso, where each row in $W$ is a group. The associated regularizer 
+then is $r(W) = \lambda\sum_j^p \|W_{j:}\|_2$ where $\lambda$ is a parameter
+that adjusts the strength of the regularization.
+This has the effect of producing a few rows of non-zero values in $W$;
+since each row corresponds to an individual feature, the optimal sparse $W^*$
+yields a fast-evaluating decision function, i.e. most features are 
+ignored at test time.
+
+To minimize this multiclass classification group lasso objective, ??? use 
+coordiante descent, iteratively solving a sub-problem with respect to a 
+single group. Figure ? shows a general outline of algorithm that involves
+computing the partial gradient with respect to the 
+current group $j$, the prox
+operator of the L2 norm, and a final line search to identify an appropriate
+step size for the current update.
+
+\begin{algorithm}
+ \For{$i \gets 1, \ldots, max\;iters $}{
+     \For{$j \gets 1, \ldots, p$}{
+        Compute gradient $l^\prime(W)_{j:}$\\
+        Choose $\mathcal{L}_j$\\
+        Compute \\
+        $\;\;\;\;V_j = W_{j:} - \frac{1}{\mathcal{L}_j}l^\prime(W)_{j:}$\\
+        $\;\;\;\;W_{j:}^* 
+          = \operatorname{Prox}_{\frac{\lambda}{\mathcal{L}_j}\|\cdot\|_j}
+         (V_j)$\\
+
+         $\;\;\;\;\delta = W_{j:}^* - W_{j:}$\\
+        Choose $\alpha$\\
+        $W_{j:} \gets W_{j:} + \alpha \delta$\\
+
+    }
+ }
+\end{algorithm}
+
+Efficient computation of this objective is possible by storing current 
+loss for each data point. Let $A$ be an $n\times k$ matrix where the 
+$i,r$-th element corresponds to 
+ $(1-(W_{:y_i}^Tx_i - W_{:r}x_i).$
+ The gradient can then be calculated as 
+ $l^\prime(W)_{j} = \frac{2}{n}\sum_{i=1}^n\sum_{r\ne y_i}
+ \max(A_{ir}, 0)(x_{ij}e_{y_i} - x_{ij} e_r)$
+where $e_r$ is a $k$ dimensional vector with zeroes everywhere except for a 1
+at the $r$-th position. We only have to examine elements in $A$ for which 
+the corresponding $x_{ij}$ is non-zero. When $x_{i}$ is sparse, more often
+than not $x_{ij}$ is zero and can be ignored.
+
 \subsection{Latent Group Lasso}
 
-\subsection{Multiclass Classification with Group Lasso}
+One limitation of group lasso is that it assumes that group assignments are
+non-overlapping. In some domains, this can be too restrictive an assumption.
+For example, in document classification, individual words are used as features.
+If we were to construct groupings of these features, we might run into a case
+where one word could reasonably be added to several groups. The overlapping or
+latent group lasso was introduced to handled such cases.
+
+??? develop a theoretical justification for the latent group lasso, as well
+as its equivalence to a regular group lasso in a higher dimensional space.
+Let $\mathcal{G}$ be the set of (possibly overlapping) groups,
+where $g \in \mathcal{G}$ is a set of indices of covariates associated with 
+that group. 
+Let our
+data consist of vectors $x_i$ in $p$ dimensions, and let $w$ be the 
+corresponding weight vector in $p$ dimensions that we would like to learn.
+Finally, define $\operatorname{supp}(v)$ to be the support of $v$, i.e.
+the indices of the non-zero elements in $v$.
+
+For each group
+$g \in \mathcal{G}$ we associate a latent vector $v^g \in \mathcal{R}^p$ where
+$\operatorname{supp}(v^g) = g$, i.e. the nonzero elements in the $v^g$ correspond
+to the indices in the group $g$. 
+The original weight vector $w$ can be
+interpreted as a sum of the latent vectors, or
+$w = \sum_{g \in \mathcal{G}} v^g$. 
+??? arrive at the following minimization
+problem 
+$$ \min_{w, v^g} l(w) + \lambda \sum_{g \in \mathcal{G}} d_g \|v^g \|_2 $$
+$$\mathrm{s.t.}\;\;\; w = \sum_g v^g$$
+
+??? show that when the original problem is regression, 
+$w^Tx = \left(\sum_g v^g\right)^Tx = \hat{v}^T \hat{x}$ where 
+$\hat{v} = (v^{g})_{g \in \mathcal{G}}$ and
+$\hat{x} = \bigoplus_{g \in \mathcal{G} } (x_i)_{i \in g}$, i.e. $\hat{x}$ is
+the restrictions of each $g$ stacked on top of each other. $\hat{x}, \hat{v}$ 
+have dimension $\sum_{g \in \mathcal{G}} |g|$ 
+In this formulation, the optimal $\hat{v}^*$ can be found using regular 
+non-overlapping group lasso.
 

### 2014-12-18 highdim-paper/paper.tex
updated aritificial data in the result section

@@
 
-$minimize_{W \in R^{d x m}} F(W) = $
-
-$\frac{1}{n} \sum_{i=1}^{n} \sum_{r \neq y_i } max(1 - W_{:y_i} \cdot x_i + W_{:r} \cdot x_i , 0 )^2 $
-
-$ + \lambda \sum_{g=1}^{|G|} \sum_{m=1}^{d} \| W_{g,m} \|_2$ \\
+$$ \min_{W \in R^{d x m}} F(W) = $$
+$$\frac{1}{n} \sum_{i=1}^{n} \sum_{r \neq y_i } \max(1 - ( W_{:y_i}^T \cdot x_i - W_{:r}^T \cdot x_i) , 0 )^2 $$
+$$ + \lambda \sum_{g \in \mathcal{G}} \sum_{r=1}^{d} \| W_{g,r} \|_2$$ \\
 
@@
 And as long as their difference is greater then a margin ($1$ in this case), we won't penalize it.
-In the second term, $W_{g,m}$ means a block of weights in group $g$ and class $m$.
-The L2 norm regulization is computed and sum up for each block.
+In the second term, $W_{g,r}$ means a block of weights in group $g$ and class $m$.
+The L2-norm regulization is computed and sum up for each block.
 The $\lambda > 0$ is a parameter controls the trade-off between the hinge loss and the L2-norm regulization.
@@
 
-\subsection{Artificial data}
+\subsection{Artificial Data}
 
@@
 \begin{center}
-	\includegraphics[natwidth=200, natheight=306]{m_img}
-	\caption{Group-wise sparse weight matrix generated: 6 classes, 30 features in 5 groups}
+	\includegraphics[width=5cm, natwidth=200, natheight=206]{m_img}
+	\caption{Group-wise sparse weight matrix generated: 5 classes, 25 features in 5 groups}
 \end{center}
@@
 
-Then we generate random vectors, each of which has the length of the number of all features, and calculate dot product with the weight matrix W to get the class assignments for these random vectors.
+Then we generate random vectors, each of which has a length of the number of all features, and calculate dot product with the weight matrix W to get the class assignments for these random vectors.
 The random vetors X and the class assignments Y make up the training data set.
@@
 \section{Results}
+
+\subsection{Newsgroup Data}
+
+\subsection{Artificial Data}
+
+Shape Recovery.
+One of the main indicator of the effectiveness of our model is to see whether the calculated weight matrix is sparse group-wise.
+Our experiments show so.
+The following figures shows in a typical trial, the generated target weight matrix and the recovered weight matrix by our model.
+By comparing them side by side, we can tell that their sparsity patterns are similar.
+
+\begin{figure}[ht]
+\begin{center}
+	\includegraphics[width=5cm, natwidth=200, natheight=307]{m1_img}
+	\caption{Target group-wise sparse weight matrix generated: 5 classes, 25 features in 5 groups}
+\end{center}
+\end{figure}
+
+\begin{figure}[ht]
+\begin{center}
+	\includegraphics[width=8cm,natwidth=200, natheight=186]{m2_img}
+	\caption{Weight matrix calculated from the training data. It's similar to the one generated.}
+\end{center}
+\end{figure}
+
+The different weights between the calculated matrix and the target matrix can be due to many factors.
+First, sample coverage is a major factor.
+In our simulation data, the sample size is small.
+Limited by the time complexity of the algorithm, it's difficult to complete the computation for a very large sample size in a reasonable time.
+Also, the sampling is random.
+There is no guaranteed that the inferred weights leads to the target weights.
+\\
+
+Accuracy.
+In our experiments, the generator algorithm was configured to produce 150 random vectors from the underlying model where it consists of 5 classes and 25 features in 5 groups.
+The accuracy achieved was about $60\%$ to $70\%$.
+\\
 

### 2014-12-18 highdim-paper/paper.tex
intro
added intro and names

--- 2014-12-18 highdim-paper/paper.tex
@@
 
-\author{name1 \\
+\author{Chris Kedzie \\
   Columbia University\\
-  {\small \tt uni1@columbia.edu} \\\And
-  name2 \\
+  {\small \tt kedzie@cs.columbia.edu} \\\And
+  Dahong Liu \\
   Columbia University\\
-  {\small \tt uni2@columbia.edu} \\\And
-  name3\\
+  {\small \tt dl2868@columbia.edu} \\\And
+  Xiao Zhu\\
   Columbia University\\
-  {\small \tt uni3@columbia.edu} \\}
+  {\small \tt xz2362@columbia.edu} \\\And
+  Yichi Zhang\\
+  Columbia University\\
+  {\small \tt yz2657@columbia.edu} \\}
 \date{}
@@
 \section{Introduction}
+We motivate our project by considering the text classification problem: 
+can we accurately classify text documents by topic. With the rapid growth 
+of online information, text categorization has become one of the key techniques 
+for handling and organizing text data. Text categorization techniques are used 
+not only to filter spam emails, as we are mostly familiar, but also to classify 
+news stories, to find interesting information on the WWW, and to guide a 
+user's search through hypertext. Since building text classifiers by hand is 
+difficult and time-consuming, it is advantageous to learn classifiers from examples. \\
+
+In this project we will use the ''20 Newsgroups'' dataset, popular in machine 
+learning literature, to explore some variants of latent group lasso for text classification. 
+This dataset contains about 20,000 documents split roughly evenly amongst the 20 
+predefined topics. Every training example comes in the form of a document-term 
+matrix $\mathbf{M}$ that is $D\times V$ where $D=11307$. The vocabulary 
+size $V= 61188$ words. \\
+
+In section 2, we will provide some background on latent group lasso and 
+multiclass classification. Latent group Lasso is based on applying the usual 
+group Lasso penalty on a set of latent variables when groups are overlapping.
+In section 3, we will present our model, which uses hinge loss for training classifiers. 
+The following sections will include detailed explanations of our datasets and the 
+results we gathered.
 

### 2014-12-18 highdim-paper/paper.tex

@@
+<<<<<<< HEAD
 %
@@
 \end{document}
+=======
+%
+% File acl2014.tex
+%
+% Contact: koller@ling.uni-potsdam.de, yusuke@nii.ac.jp
+%%
+%% Based on the style files for ACL-2013, which were, in turn,
+%% Based on the style files for ACL-2012, which were, in turn,
+%% based on the style files for ACL-2011, which were, in turn, 
+%% based on the style files for ACL-2010, which were, in turn, 
+%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
+%% based on the style files for EACL-2009 and IJCNLP-2008...
+
+%% Based on the style files for EACL 2006 by 
+%%e.agirre@ehu.es or Sergi.Balari@uab.es
+%% and that of ACL 08 by Joakim Nivre and Noah Smith
+
+\documentclass[11pt]{article}
+\usepackage{acl2014}
+\usepackage{times}
+\usepackage{url}
+\usepackage{latexsym}
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage[]{algorithm2e}
+
+\DeclareGraphicsExtensions{.pdf,.png,.jpg}
+
+%\setlength\titlebox{5cm}
+
+% You can expand the titlebox if you need extra space
+% to show all the authors. Please do not make the titlebox
+% smaller than 5cm (the original size); we will check this
+% in the camera-ready version and ask you to change it back.
+
+\title{High-Dim Project}
+
+\author{name1 \\
+  Columbia University\\
+  {\small \tt uni1@columbia.edu} \\\And
+  name2 \\
+  Columbia University\\
+  {\small \tt uni2@columbia.edu} \\\And
+  name3\\
+  Columbia University\\
+  {\small \tt uni3@columbia.edu} \\}
+\date{}
+
+\begin{document}
+\maketitle
+%\begin{abstract}
+%  This document contains the instructions for preparing a camera-ready
+%  manuscript for the proceedings of ACL-2014. The document itself
+%  conforms to its own specifications, and is therefore an example of
+%  what your manuscript should look like. These instructions should be
+%  used for both papers submitted for review and for final versions of
+%  accepted papers.  Authors are asked to conform to all the directions
+%  reported in this document.
+%\end{abstract}
+
+\section{Introduction}
+
+\section{Background}
+
+\subsection{Multiclass Classification with Group Lasso}
+
+The task of multiclass classification involves the prediction of a class label
+$l$ where the number of possible labels is $k>2$. More often than not, the 
+original problem is transformed into $k$ binary classification problems, i.e.
+$1$--vs.--all classification and positive prediction with the highest 
+confidence is selected as the label. This approach has the disadvantage of
+having to train $k$ different models.
+
+An alternative formulation, direct multiclass classification, tackles this 
+problem directly by solving the following $\operatorname{argmax}$ problem:
+$$y_i = \operatorname{argmax}_c W_{:c}^T x_i $$
+where $W \in \mathcal{R}^{p \times k}$ is a weight matrix, with $W_{ij}$
+corresponding to the $i$-th feature of class $j$. In this paper, we refer
+to features as elements in the instance data $x$. A feature in $x$ is
+associated with $k$ weights in $W$, one for each class.
+
+The decision function above suggests a max-margin style loss function. More
+specifically, we use the squared hinge loss:
+
+$$ l(W) = \sum_{i=1}^n \sum_{r\ne y_i}^k 
+    \max\left(1 - (W_{:y_i}^Tx_i - W_{:r}^Tx_i), 0\right)^2 $$
+
+The minimization of $l$ directly will lead to a minimizer $W^*$ that is
+dense. Sparse solutions are often explicitly sought, with model compactness
+leading to fast prediction at test time. In order to obtain a sparse $W^*$,
+a regularization term $r(W)$ is often applied, yielding the objective 
+function:
+
+$$\min_W l(W) + r(W).$$
+
+Many choices are available for the regularizer $r$. In (ref ???), they use
+the group lasso, where each row in $W$ is a group. The associated regularizer 
+then is $r(W) = \lambda\sum_j^p \|W_{j:}\|_2$ where $\lambda$ is a parameter
+that adjusts the strength of the regularization.
+This has the effect of producing a few rows of non-zero values in $W$;
+since each row corresponds to an individual feature, the optimal sparse $W^*$
+yields a fast-evaluating decision function, i.e. most features are 
+ignored at test time.
+
+To minimize this multiclass classification group lasso objective, ??? use 
+coordiante descent, iteratively solving a sub-problem with respect to a 
+single group. Figure ? shows a general outline of algorithm that involves
+computing the partial gradient with respect to the 
+current group $j$, the prox
+operator of the L2 norm, and a final line search to identify an appropriate
+step size for the current update.
+
+\begin{algorithm}
+ \For{$i \gets 1, \ldots, max\;iters $}{
+     \For{$j \gets 1, \ldots, p$}{
+        Compute gradient $l^\prime(W)_{j:}$\\
+        Choose $\mathcal{L}_j$\\
+        Compute \\
+        $\;\;\;\;V_j = W_{j:} - \frac{1}{\mathcal{L}_j}l^\prime(W)_{j:}$\\
+        $\;\;\;\;W_{j:}^* 
+          = \operatorname{Prox}_{\frac{\lambda}{\mathcal{L}_j}\|\cdot\|_j}
+         (V_j)$\\
+
+         $\;\;\;\;\delta = W_{j:}^* - W_{j:}$\\
+        Choose $\alpha$\\
+        $W_{j:} \gets W_{j:} + \alpha \delta$\\
+
+    }
+ }
+\end{algorithm}
+
+Efficient computation of this objective is possible by storing current 
+loss for each data point. Let $A$ be an $n\times k$ matrix where the 
+$i,r$-th element corresponds to 
+ $(1-(W_{:y_i}^Tx_i - W_{:r}x_i).$
+ The gradient can then be calculated as 
+ $l^\prime(W)_{j} = \frac{2}{n}\sum_{i=1}^n\sum_{r\ne y_i}
+ \max(A_{ir}, 0)(x_{ij}e_{y_i} - x_{ij} e_r)$
+where $e_r$ is a $k$ dimensional vector with zeroes everywhere except for a 1
+at the $r$-th position. We only have to examine elements in $A$ for which 
+the corresponding $x_{ij}$ is non-zero. When $x_{i}$ is sparse, more often
+than not $x_{ij}$ is zero and can be ignored.
+
+\subsection{Latent Group Lasso}
+
+One limitation of group lasso is that it assumes that group assignments are
+non-overlapping. In some domains, this can be too restrictive an assumption.
+For example, in document classification, individual words are used as features.
+If we were to construct groupings of these features, we might run into a case
+where one word could reasonably be added to several groups. The overlapping or
+latent group lasso was introduced to handled such cases.
+
+??? develop a theoretical justification for the latent group lasso, as well
+as its equivalence to a regular group lasso in a higher dimensional space.
+Let $\mathcal{G}$ be the set of (possibly overlapping) groups,
+where $g \in \mathcal{G}$ is a set of indices of covariates associated with 
+that group. 
+Let our
+data consist of vectors $x_i$ in $p$ dimensions, and let $w$ be the 
+corresponding weight vector in $p$ dimensions that we would like to learn.
+Finally, define $\operatorname{supp}(v)$ to be the support of $v$, i.e.
+the indices of the non-zero elements in $v$.
+
+For each group
+$g \in \mathcal{G}$ we associate a latent vector $v^g \in \mathcal{R}^p$ where
+$\operatorname{supp}(v^g) = g$, i.e. the nonzero elements in the $v^g$ correspond
+to the indices in the group $g$. 
+The original weight vector $w$ can be
+interpreted as a sum of the latent vectors, or
+$w = \sum_{g \in \mathcal{G}} v^g$. 
+??? arrive at the following minimization
+problem 
+$$ \min_{w, v^g} l(w) + \lambda \sum_{g \in \mathcal{G}} d_g \|v^g \|_2 $$
+$$\mathrm{s.t.}\;\;\; w = \sum_g v^g$$
+
+??? show that when the original problem is regression, 
+$w^Tx = \left(\sum_g v^g\right)^Tx = \hat{v}^T \hat{x}$ where 
+$\hat{v} = (v^{g})_{g \in \mathcal{G}}$ and
+$\hat{x} = \bigoplus_{g \in \mathcal{G} } (x_i)_{i \in g}$, i.e. $\hat{x}$ is
+the restrictions of each $g$ stacked on top of each other. $\hat{x}, \hat{v}$ 
+have dimension $\sum_{g \in \mathcal{G}} |g|$ 
+In this formulation, the optimal $\hat{v}^*$ can be found using regular 
+non-overlapping group lasso.
+
+\section{Our Model}
+
+Given n training vectors $x_i \in R_d$ and their class labels $y_i \in \{1, ..., m\}$, our goal is to compute $W$ such that it maximizes the accurarcy of our prediction and it is group-wise sparse. \\
+
+In our model, we minimize the following objective function : \\
+
+$$ \min_{W \in R^{d x m}} F(W) = $$
+$$\frac{1}{n} \sum_{i=1}^{n} \sum_{r \neq y_i } \max(1 - ( W_{:y_i}^T \cdot x_i - W_{:r}^T \cdot x_i) , 0 )^2 $$
+$$ + \lambda \sum_{g \in \mathcal{G}} \sum_{r=1}^{d} \| W_{g,r} \|_2$$ \\
+
+The first term is the multiclass squared hinge loss function.
+We want the dot product of an instance and its feature vector to be as large as possible, and the dot product of this instance and the rest feature vectors to be as small as possible.
+And as long as their difference is greater then a margin ($1$ in this case), we won't penalize it.
+In the second term, $W_{g,r}$ means a block of weights in group $g$ and class $m$.
+The L2-norm regulization is computed and sum up for each block.
+The $\lambda > 0$ is a parameter controls the trade-off between the hinge loss and the L2-norm regulization.
+\\
+
+\section{Data}
+
+\subsection{Newsgroup Data}
+
+\subsubsection{Group Identification}
+
+\subsection{Artificial Data}
+
+For the datasets described above, we can't tell with 100 percent confidence that the datasets follow the assumptions of the group structures for the features.
+And even if they are indeed structured that way, we maybe wrong with the method of coming up with the groups.
+These issues make it difficult to access our model.\\
+
+To get rid of all these problems and validate the effectiveness of our model, we created artificial data that followed the underlying assumptions of the model.
+First, we generate a sparse weight matrix W to represent the relationship between features and classes.
+The weight matrix W has an internal structure in which features are grouped together.
+And also, only a small number of groups have non-zero weights.
+This makes the matrix sparse.\\
+
+\begin{figure}[ht]
+\begin{center}
+	\includegraphics[width=5cm, natwidth=200, natheight=206]{m_img}
+	\caption{Group-wise sparse weight matrix generated: 5 classes, 25 features in 5 groups}
+\end{center}
+\end{figure}
+
+Then we generate random vectors, each of which has a length of the number of all features, and calculate dot product with the weight matrix W to get the class assignments for these random vectors.
+The random vetors X and the class assignments Y make up the training data set.
+\\
+
+Our goal is to infer this weight matrix W from X and Y using our model.
+By generating the data set using this method, we can test the effectiveness of our model on a noiseless dataset with right underlying assumptions.\\
+
+\section{Results}
+
+\subsection{Newsgroup Data}
+
+\subsection{Artificial Data}
+
+Shape Recovery.
+One of the main indicator of the effectiveness of our model is to see whether the calculated weight matrix is sparse group-wise.
+Our experiments show so.
+The following figures shows in a typical trial, the generated target weight matrix and the recovered weight matrix by our model.
+By comparing them side by side, we can tell that their sparsity patterns are similar.
+
+\begin{figure}[ht]
+\begin{center}
+	\includegraphics[width=5cm, natwidth=200, natheight=307]{m1_img}
+	\caption{Target group-wise sparse weight matrix generated: 5 classes, 25 features in 5 groups}
+\end{center}
+\end{figure}
+
+\begin{figure}[ht]
+\begin{center}
+	\includegraphics[width=8cm,natwidth=200, natheight=186]{m2_img}
+	\caption{Weight matrix calculated from the training data. It's similar to the one generated.}
+\end{center}
+\end{figure}
+
+The different weights between the calculated matrix and the target matrix can be due to many factors.
+First, sample coverage is a major factor.
+In our simulation data, the sample size is small.
+Limited by the time complexity of the algorithm, it's difficult to complete the computation for a very large sample size in a reasonable time.
+Also, the sampling is random.
+There is no guaranteed that the inferred weights leads to the target weights.
+\\
+
+Accuracy.
+In our experiments, the generator algorithm was configured to produce 150 random vectors from the underlying model where it consists of 5 classes and 25 features in 5 groups.
+The accuracy achieved was about $60\%$ to $70\%$.
+\\
+
+\section{Conclusion}
+% include your own bib file like this:
+%\bibliographystyle{acl}
+%\bibliography{acl2014}
+
+%\begin{thebibliography}{}
+%
+%\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
+%Alfred~V. Aho and Jeffrey~D. Ullman.
+%\newblock 1972.
+%\newblock {\em The Theory of Parsing, Translation and Compiling}, volume~1.
+%\newblock Prentice-{Hall}, Englewood Cliffs, NJ.
+%
+%\bibitem[\protect\citename{{American Psychological Association}}1983]{APA:83}
+%{American Psychological Association}.
+%\newblock 1983.
+%\newblock {\em Publications Manual}.
+%\newblock American Psychological Association, Washington, DC.
+%
+%\bibitem[\protect\citename{{Association for Computing Machinery}}1983]{ACM:83}
+%{Association for Computing Machinery}.
+%\newblock 1983.
+%\newblock {\em Computing Reviews}, 24(11):503--512.
+%
+%\bibitem[\protect\citename{Chandra \bgroup et al.\egroup }1981]{Chandra:81}
+%Ashok~K. Chandra, Dexter~C. Kozen, and Larry~J. Stockmeyer.
+%\newblock 1981.
+%\newblock Alternation.
+%\newblock {\em Journal of the Association for Computing Machinery},
+%  28(1):114--133.
+%
+%\bibitem[\protect\citename{Gusfield}1997]{Gusfield:97}
+%Dan Gusfield.
+%\newblock 1997.
+%\newblock {\em Algorithms on Strings, Trees and Sequences}.
+%\newblock Cambridge University Press, Cambridge, UK.
+%
+%\end{thebibliography}
+
+\end{document}
+>>>>>>> FETCH_HEAD

### 2014-12-18 highdim-paper/paper.tex
Fixed the previous merge issue

@@
-<<<<<<< HEAD
 %
@@
 results we gathered.
-
-\section{Background}
-
-\subsection{Multiclass Classification with Group Lasso}
-
-The task of multiclass classification involves the prediction of a class label
-$l$ where the number of possible labels is $k>2$. More often than not, the 
-original problem is transformed into $k$ binary classification problems, i.e.
-$1$--vs.--all classification and positive prediction with the highest 
-confidence is selected as the label. This approach has the disadvantage of
-having to train $k$ different models.
-
-An alternative formulation, direct multiclass classification, tackles this 
-problem directly by solving the following $\operatorname{argmax}$ problem:
-$$y_i = \operatorname{argmax}_c W_{:c}^T x_i $$
-where $W \in \mathcal{R}^{p \times k}$ is a weight matrix, with $W_{ij}$
-corresponding to the $i$-th feature of class $j$. In this paper, we refer
-to features as elements in the instance data $x$. A feature in $x$ is
-associated with $k$ weights in $W$, one for each class.
-
-The decision function above suggests a max-margin style loss function. More
-specifically, we use the squared hinge loss:
-
-$$ l(W) = \sum_{i=1}^n \sum_{r\ne y_i}^k 
-    \max\left(1 - (W_{:y_i}^Tx_i - W_{:r}^Tx_i), 0\right)^2 $$
-
-The minimization of $l$ directly will lead to a minimizer $W^*$ that is
-dense. Sparse solutions are often explicitly sought, with model compactness
-leading to fast prediction at test time. In order to obtain a sparse $W^*$,
-a regularization term $r(W)$ is often applied, yielding the objective 
-function:
-
-$$\min_W l(W) + r(W).$$
-
-Many choices are available for the regularizer $r$. In (ref ???), they use
-the group lasso, where each row in $W$ is a group. The associated regularizer 
-then is $r(W) = \lambda\sum_j^p \|W_{j:}\|_2$ where $\lambda$ is a parameter
-that adjusts the strength of the regularization.
-This has the effect of producing a few rows of non-zero values in $W$;
-since each row corresponds to an individual feature, the optimal sparse $W^*$
-yields a fast-evaluating decision function, i.e. most features are 
-ignored at test time.
-
-To minimize this multiclass classification group lasso objective, ??? use 
-coordiante descent, iteratively solving a sub-problem with respect to a 
-single group. Figure ? shows a general outline of algorithm that involves
-computing the partial gradient with respect to the 
-current group $j$, the prox
-operator of the L2 norm, and a final line search to identify an appropriate
-step size for the current update.
-
-\begin{algorithm}
- \For{$i \gets 1, \ldots, max\;iters $}{
-     \For{$j \gets 1, \ldots, p$}{
-        Compute gradient $l^\prime(W)_{j:}$\\
-        Choose $\mathcal{L}_j$\\
-        Compute \\
-        $\;\;\;\;V_j = W_{j:} - \frac{1}{\mathcal{L}_j}l^\prime(W)_{j:}$\\
-        $\;\;\;\;W_{j:}^* 
-          = \operatorname{Prox}_{\frac{\lambda}{\mathcal{L}_j}\|\cdot\|_j}
-         (V_j)$\\
-
-         $\;\;\;\;\delta = W_{j:}^* - W_{j:}$\\
-        Choose $\alpha$\\
-        $W_{j:} \gets W_{j:} + \alpha \delta$\\
-
-    }
- }
-\end{algorithm}
-
-Efficient computation of this objective is possible by storing current 
-loss for each data point. Let $A$ be an $n\times k$ matrix where the 
-$i,r$-th element corresponds to 
- $(1-(W_{:y_i}^Tx_i - W_{:r}x_i).$
- The gradient can then be calculated as 
- $l^\prime(W)_{j} = \frac{2}{n}\sum_{i=1}^n\sum_{r\ne y_i}
- \max(A_{ir}, 0)(x_{ij}e_{y_i} - x_{ij} e_r)$
-where $e_r$ is a $k$ dimensional vector with zeroes everywhere except for a 1
-at the $r$-th position. We only have to examine elements in $A$ for which 
-the corresponding $x_{ij}$ is non-zero. When $x_{i}$ is sparse, more often
-than not $x_{ij}$ is zero and can be ignored.
-
-\subsection{Latent Group Lasso}
-
-One limitation of group lasso is that it assumes that group assignments are
-non-overlapping. In some domains, this can be too restrictive an assumption.
-For example, in document classification, individual words are used as features.
-If we were to construct groupings of these features, we might run into a case
-where one word could reasonably be added to several groups. The overlapping or
-latent group lasso was introduced to handled such cases.
-
-??? develop a theoretical justification for the latent group lasso, as well
-as its equivalence to a regular group lasso in a higher dimensional space.
-Let $\mathcal{G}$ be the set of (possibly overlapping) groups,
-where $g \in \mathcal{G}$ is a set of indices of covariates associated with 
-that group. 
-Let our
-data consist of vectors $x_i$ in $p$ dimensions, and let $w$ be the 
-corresponding weight vector in $p$ dimensions that we would like to learn.
-Finally, define $\operatorname{supp}(v)$ to be the support of $v$, i.e.
-the indices of the non-zero elements in $v$.
-
-For each group
-$g \in \mathcal{G}$ we associate a latent vector $v^g \in \mathcal{R}^p$ where
-$\operatorname{supp}(v^g) = g$, i.e. the nonzero elements in the $v^g$ correspond
-to the indices in the group $g$. 
-The original weight vector $w$ can be
-interpreted as a sum of the latent vectors, or
-$w = \sum_{g \in \mathcal{G}} v^g$. 
-??? arrive at the following minimization
-problem 
-$$ \min_{w, v^g} l(w) + \lambda \sum_{g \in \mathcal{G}} d_g \|v^g \|_2 $$
-$$\mathrm{s.t.}\;\;\; w = \sum_g v^g$$
-
-??? show that when the original problem is regression, 
-$w^Tx = \left(\sum_g v^g\right)^Tx = \hat{v}^T \hat{x}$ where 
-$\hat{v} = (v^{g})_{g \in \mathcal{G}}$ and
-$\hat{x} = \bigoplus_{g \in \mathcal{G} } (x_i)_{i \in g}$, i.e. $\hat{x}$ is
-the restrictions of each $g$ stacked on top of each other. $\hat{x}, \hat{v}$ 
-have dimension $\sum_{g \in \mathcal{G}} |g|$ 
-In this formulation, the optimal $\hat{v}^*$ can be found using regular 
-non-overlapping group lasso.
-
-\section{Our Model}
-
-Given n training vectors $x_i \in R_d$ and their class labels $y_i \in \{1, ..., m\}$, our goal is to compute $W$ such that it maximizes the accurarcy of our prediction and it is group-wise sparse. \\
-
-In our model, we minimize the following objective function : \\
-
-$minimize_{W \in R^{d x m}} F(W) = $
-
-$\frac{1}{n} \sum_{i=1}^{n} \sum_{r \neq y_i } max(1 - W_{:y_i} \cdot x_i + W_{:r} \cdot x_i , 0 )^2 $
-
-$ + \lambda \sum_{g=1}^{|G|} \sum_{m=1}^{d} \| W_{g,m} \|_2$ \\
-
-The first term is the multiclass squared hinge loss function.
-We want the dot product of an instance and its feature vector to be as large as possible, and the dot product of this instance and the rest feature vectors to be as small as possible.
-And as long as their difference is greater then a margin ($1$ in this case), we won't penalize it.
-In the second term, $W_{g,m}$ means a block of weights in group $g$ and class $m$.
-The L2 norm regulization is computed and sum up for each block.
-The $\lambda > 0$ is a parameter controls the trade-off between the hinge loss and the L2-norm regulization.
-\\
-
-\section{Data}
-
-\subsection{Newsgroup Data}
-
-\subsubsection{Group Identification}
-
-\subsection{Artificial data}
-
-For the datasets described above, we can't tell with 100 percent confidence that the datasets follow the assumptions of the group structures for the features.
-And even if they are indeed structured that way, we maybe wrong with the method of coming up with the groups.
-These issues make it difficult to access our model.\\
-
-To get rid of all these problems and validate the effectiveness of our model, we created artificial data that followed the underlying assumptions of the model.
-First, we generate a sparse weight matrix W to represent the relationship between features and classes.
-The weight matrix W has an internal structure in which features are grouped together.
-And also, only a small number of groups have non-zero weights.
-This makes the matrix sparse.\\
-
-\begin{figure}[ht]
-\begin{center}
-	\includegraphics[natwidth=200, natheight=306]{m_img}
-	\caption{Group-wise sparse weight matrix generated: 6 classes, 30 features in 5 groups}
-\end{center}
-\end{figure}
-
-Then we generate random vectors, each of which has the length of the number of all features, and calculate dot product with the weight matrix W to get the class assignments for these random vectors.
-The random vetors X and the class assignments Y make up the training data set.
-\\
-
-Our goal is to infer this weight matrix W from X and Y using our model.
-By generating the data set using this method, we can test the effectiveness of our model on a noiseless dataset with right underlying assumptions.\\
-
-\section{Results}
-
-\section{Conclusion}
-% include your own bib file like this:
-%\bibliographystyle{acl}
-%\bibliography{acl2014}
-
-%\begin{thebibliography}{}
-%
-%\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
-%Alfred~V. Aho and Jeffrey~D. Ullman.
-%\newblock 1972.
-%\newblock {\em The Theory of Parsing, Translation and Compiling}, volume~1.
-%\newblock Prentice-{Hall}, Englewood Cliffs, NJ.
-%
-%\bibitem[\protect\citename{{American Psychological Association}}1983]{APA:83}
-%{American Psychological Association}.
-%\newblock 1983.
-%\newblock {\em Publications Manual}.
-%\newblock American Psychological Association, Washington, DC.
-%
-%\bibitem[\protect\citename{{Association for Computing Machinery}}1983]{ACM:83}
-%{Association for Computing Machinery}.
-%\newblock 1983.
-%\newblock {\em Computing Reviews}, 24(11):503--512.
-%
-%\bibitem[\protect\citename{Chandra \bgroup et al.\egroup }1981]{Chandra:81}
-%Ashok~K. Chandra, Dexter~C. Kozen, and Larry~J. Stockmeyer.
-%\newblock 1981.
-%\newblock Alternation.
-%\newblock {\em Journal of the Association for Computing Machinery},
-%  28(1):114--133.
-%
-%\bibitem[\protect\citename{Gusfield}1997]{Gusfield:97}
-%Dan Gusfield.
-%\newblock 1997.
-%\newblock {\em Algorithms on Strings, Trees and Sequences}.
-%\newblock Cambridge University Press, Cambridge, UK.
-%
-%\end{thebibliography}
-
-\end{document}
-=======
-%
-% File acl2014.tex
-%
-% Contact: koller@ling.uni-potsdam.de, yusuke@nii.ac.jp
-%%
-%% Based on the style files for ACL-2013, which were, in turn,
-%% Based on the style files for ACL-2012, which were, in turn,
-%% based on the style files for ACL-2011, which were, in turn, 
-%% based on the style files for ACL-2010, which were, in turn, 
-%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
-%% based on the style files for EACL-2009 and IJCNLP-2008...
-
-%% Based on the style files for EACL 2006 by 
-%%e.agirre@ehu.es or Sergi.Balari@uab.es
-%% and that of ACL 08 by Joakim Nivre and Noah Smith
-
-\documentclass[11pt]{article}
-\usepackage{acl2014}
-\usepackage{times}
-\usepackage{url}
-\usepackage{latexsym}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage[]{algorithm2e}
-
-\DeclareGraphicsExtensions{.pdf,.png,.jpg}
-
-%\setlength\titlebox{5cm}
-
-% You can expand the titlebox if you need extra space
-% to show all the authors. Please do not make the titlebox
-% smaller than 5cm (the original size); we will check this
-% in the camera-ready version and ask you to change it back.
-
-\title{High-Dim Project}
-
-\author{name1 \\
-  Columbia University\\
-  {\small \tt uni1@columbia.edu} \\\And
-  name2 \\
-  Columbia University\\
-  {\small \tt uni2@columbia.edu} \\\And
-  name3\\
-  Columbia University\\
-  {\small \tt uni3@columbia.edu} \\}
-\date{}
-
-\begin{document}
-\maketitle
-%\begin{abstract}
-%  This document contains the instructions for preparing a camera-ready
-%  manuscript for the proceedings of ACL-2014. The document itself
-%  conforms to its own specifications, and is therefore an example of
-%  what your manuscript should look like. These instructions should be
-%  used for both papers submitted for review and for final versions of
-%  accepted papers.  Authors are asked to conform to all the directions
-%  reported in this document.
-%\end{abstract}
-
-\section{Introduction}
 
@@
 \end{document}
->>>>>>> FETCH_HEAD

### 2014-12-18 highdim-paper/paper.tex
figure
updated lambda-accuracy plot

@@
 \usepackage[]{algorithm2e}
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 In section 3, we will present our model, which uses hinge loss for training classifiers. 
-The following sections will include detailed explanations of our datasets and the 
+The latter sections will include detailed explanations of our datasets and the 
 results we gathered.
@@
 \begin{center}
-	\includegraphics[width=5cm, natwidth=200, natheight=206]{m_img}
+	\includegraphics[width=.5\linewidth]{m_img}
 	\caption{Group-wise sparse weight matrix generated: 5 classes, 25 features in 5 groups}
@@
 \begin{figure}[ht]
-\begin{center}
-	\includegraphics[width=5cm, natwidth=200, natheight=307]{m1_img}
+  \centering
+  \includegraphics[width=.5\linewidth]{m1_img}
   \caption{Target group-wise sparse weight matrix generated: 5 classes, 25 features in 5 groups}
-\end{center}
-\end{figure}
+\end{figure}%
 
 \begin{figure}[ht]
-\begin{center}
-	\includegraphics[width=8cm,natwidth=200, natheight=186]{m2_img}
+  \centering
+  \includegraphics[width=.9\linewidth]{m2_img}
   \caption{Weight matrix calculated from the training data. It's similar to the one generated.}
-\end{center}
 \end{figure}
@@
 In our experiments, the generator algorithm was configured to produce 150 random vectors from the underlying model where it consists of 5 classes and 25 features in 5 groups.
-The accuracy achieved was about $60\%$ to $70\%$.
-\\
+The accuracy achieved is closely related to the L2-norm regularization constant $\lambda$.
+The following figure shows the relation between lambda-accuracy and lambda-density.\\
+
+\begin{figure}[ht]
+\begin{center}
+	\includegraphics[width=\linewidth]{m3_img}
+	\caption{lambda-accuracy and lambda-density plot (150 samples, 5 classes, 25 features in 5 groups)}
+\end{center}
+\end{figure}
 

### 2014-12-18 highdim-paper/gen_pdf.sh

@@ -1,2 +1,3 @@
-latex paper.tex && dvipdfm paper.dvi
+#latex paper.tex && dvipdfm paper.dvi
+pdflatex paper.tex
 

### 2014-12-18 highdim-paper/paper.tex
Added some bits on newsgroup data section

@@
 
+We experiment on the 20 newsgroups data, a collection of topically grouped 
+email messages. 
+Because we were having issues with speed, we selected 3 topics yielding
+about 1600 documents evenly split.
+To transform the documents into a vector representation 
+suitable for our task, we first filter out any non alpha-numeric characters
+and message headers. Words were then stemmed with the Porter stemmer. 
+Words occuring fewer than 5 times were removed.
+We finally convert each document into a vector of tf-idf weights.
+The final dimensionality of this data was about 2,600.
+
 \subsubsection{Group Identification}
+
+To create groups, we first clustered the documents using k-means clustering.
+For each cluster we formed a feature group by taking the complete set of 
+non-zero features for each document in the group.
+
+We then used these feature groups to created a higher dimensional dataset of
+duplicate features with non-overlapping groups, so that we could apply our
+non-overlapping group lasso method to it.
 

### 2014-12-18 get_3ng_aug_data.py
updated get 3ng aug data method

@@ -1,0 +1,123 @@
+
+
+import numpy as np
+import re
+from sklearn.datasets import fetch_20newsgroups
+from sklearn.feature_extraction.text import TfidfVectorizer, TfidfTransformer
+from sklearn.feature_extraction import DictVectorizer
+import scipy
+from sklearn.neighbors import KDTree, NearestNeighbors
+from nltk import PorterStemmer
+
+def get_data():
+	stem = PorterStemmer().stem_word
+
+	newsgroups_train = fetch_20newsgroups(
+		categories=['alt.atheism', 'comp.graphics', 'misc.forsale'],
+		subset='train', remove=('headers', 'footers', 'quotes'))
+
+	newsgroups_train.data = newsgroups_train.data[0:200]
+	newsgroups_train.target = newsgroups_train.target[0:200]
+
+	f = open("stopwords")
+	lines = f.readlines()
+	stoplist = set([ line.strip() for line in lines])
+
+	##### get word frequency ####
+	word_pattern = re.compile(r"^[a-z]+$")
+
+	texts = [[stem(word) for word in document.lower().split()
+				if word_pattern.match(word)!= None and
+				word not in stoplist and
+				len(word)>1 ]
+				for document in newsgroups_train.data]
+
+	word_counts ={}
+	for text in texts:
+		for w in text:
+			word_counts[w] = word_counts.get(w,0) + 1 
+
+	min_count = 5 
+	infrequent_words = set()
+
+	for word, count in word_counts.iteritems():
+		if(count < min_count):
+			infrequent_words.add(word)
+
+	##### filter out infrequent words ####
+	texts = [{word: word_counts[word] for word in text 
+				if word not in infrequent_words}
+				for text in texts]
+
+	print len(texts)
+
+	vec = DictVectorizer(dtype=np.int32)
+	X_train = vec.fit_transform(texts)
+
+	trans = TfidfTransformer()
+	X_train = trans.fit_transform(X_train)
+
+	print X_train.shape
+
+	y_train = newsgroups_train.target
+
+	X_train_bin = X_train.copy()
+	##############################
+
+	import heapq
+
+
+	def sim_words(XX, row_i,already_chosen):
+		row = row_i
+		words = []
+		t = []
+		top_size = 10
+		for i in xrange(XX.shape[0]):
+			if ( i == row_i):
[…]

### 2014-12-18 ogroup_test_3ng.py

@@ -1,0 +1,46 @@
+
+
+import scipy.sparse
+from sklearn.datasets import fetch_20newsgroups
+from sklearn.feature_extraction.text import TfidfVectorizer
+from time import time
+from lightning.classification import CDClassifier
+import baseline
+import ogroup
+
+
+import random
+import numpy as np
+from sklearn.utils.extmath import safe_sparse_dot
+
+import get_3ng_aug_data as ng
+
+Xnew, y_train, groups, dict_text = ng.get_data()
+
+X_train = Xnew
+y_train = y_train
+
+
+print "### BASELINE GROUP LASSO in pure python/numpy###"
+X = X_train
+y = y_train
+clf = ogroup.BaselineGroupLasso(max_iter=30, alpha=.1,  max_steps=30)
+clf.fit(X, y, groups)
+print "Acc:", clf.score(X, y)
+print (clf.coefs_)
+
+
+print "### Equivalent Lightning Cython Implementation ###"
+light_clf = CDClassifier(penalty="l1/l2",
+                         loss="squared_hinge",
+                         multiclass=True,
+                         max_iter=clf.max_iter,
+                         alpha=1e-4, # clf.alpha,
+                         C=1.0 / X.shape[0],
+                         tol=clf.tol,
+                         permute=False,
+                         verbose=3,
+                         random_state=0).fit(X, y)
+print "Acc:", light_clf.score(X, y)
+print (light_clf.coef_.T)
+

### 2014-12-18 plot1.m

@@ -1,0 +1,19 @@
+
+
+close all;
+
+lambda =    [0.5,   0.2,    0.1,    0.05,   0.01    ]
+density =   [7/25,  13/25,  13/25,  22/25,  25/25   ]
+accurarcy = [0.593, 0.7,    0.833,  0.933,  0.993   ]
+
+figure;
+
+%plot(lambda,density , '-r')
+%line(lambda,accurarcy)
+
+plot(lambda,density,'-ro',lambda,accurarcy,'-xb')
+legend('density','accurarcy')
+xlabel('lambda')
+
+
+

### 2014-12-18 ogroup_test_3ng.py
decreased C. great result

@@ -24,7 +24,7 @@ y_train = y_train
 print "### BASELINE GROUP LASSO in pure python/numpy###"
 X = X_train
 y = y_train
-clf = ogroup.BaselineGroupLasso(max_iter=30, alpha=.1,  max_steps=30)
+clf = ogroup.BaselineGroupLasso(max_iter=30, alpha=.01,  max_steps=30)
 clf.fit(X, y, groups)
 print "Acc:", clf.score(X, y)
 print (clf.coefs_)

### 2014-12-18 ogroup_test_3ng.py
print out key words

@@ -15,6 +15,8 @@ from sklearn.utils.extmath import safe_sparse_dot
 
 import get_3ng_aug_data as ng
 
+np.set_printoptions(precision=4)
+
 Xnew, y_train, groups, dict_text = ng.get_data()
 
 X_train = Xnew
@@ -24,11 +26,26 @@ y_train = y_train
 print "### BASELINE GROUP LASSO in pure python/numpy###"
 X = X_train
 y = y_train
-clf = ogroup.BaselineGroupLasso(max_iter=30, alpha=.01,  max_steps=30)
+clf = ogroup.BaselineGroupLasso(max_iter=50, alpha=.01,  max_steps=50)
 clf.fit(X, y, groups)
 print "Acc:", clf.score(X, y)
 print (clf.coefs_)
 
+
+import heapq
+
+top_words =  30
+
+for m in xrange(clf.coefs_.shape[1]):
+	t = []
+	print 'Topic',m
+	for row in xrange(clf.coefs_.shape[0]):
+		if( clf.coefs_[row,m] >0):
+			t.append( dict_text[row])
+	for k in heapq.nlargest(top_words,t):
+		print k,
+	print
+ 
 
 print "### Equivalent Lightning Cython Implementation ###"
 light_clf = CDClassifier(penalty="l1/l2",
@@ -43,4 +60,5 @@ light_clf = CDClassifier(penalty="l1/l2",
                          random_state=0).fit(X, y)
 print "Acc:", light_clf.score(X, y)
 print (light_clf.coef_.T)
+
 

### 2014-12-18 ogroup_test_syn.py

@@ -61,7 +61,7 @@ y_train = y_pred
 print "### BASELINE GROUP LASSO in pure python/numpy###"
 X = X_train
 y = y_train
-clf = ogroup.BaselineGroupLasso(max_iter=30, alpha=.8, max_steps=30)
+clf = ogroup.BaselineGroupLasso(max_iter=30, alpha=.1, max_steps=30)
 clf.fit(X, y, groups)
 print "Acc:", clf.score(X, y)
 print (clf.coefs_)

### 2014-12-19 highdim-paper/paper.tex
Added results to the new groups section

@@
 duplicate features with non-overlapping groups, so that we could apply our
-non-overlapping group lasso method to it.
+non-overlapping group lasso method to it.\\
+
+%co-occurence matrix
+Another way to create groups for features is to use information in the co-occurence matrix.
+An co-occurence matrix is a n by n symmetric matrix, where $n$ here is the number of all the features.
+A cell in row $i$, column $j$ represents the frequency that feature $i$ and feature $j$ appear at the same time in articles.
+The co-occurence matrix is computed from $M^T M$, where $M$ is the document-to-feature matrix.
+\\
+
+Given the co-occurence matrix $Z$, a simple greedy algorithm below is used to generates groups for the features.
+
+\begin{algorithm}
+  \For{$i \gets 0, \ldots, rows(Z) $}{
+	   Get the indices of the N largest columns from row i\\
+       Output these indices to a new group\\
+       Mark all cell in these columns in the matrix Z to be 0.\\
+  }
+\end{algorithm}
+
+Groups created from this method are more meaning semantically and more granular.
+Further granularty can be achieved by couting the frequency of two features in sentence level other than article level.\\
 
@@
 \subsection{Newsgroup Data}
+
+Given limited resources, in our experiments we randomly select 200 articles from 3 news groups as the training data set.
+The selected articles are pre-processed to remove invalid words, stop words, low-frequency words.
+The co-occurence matrix method is used to generates groups.
+The maximal number of features in a group is set to 10.
+There are 37 groups created from the training data set.
+Then, all the features are re-ordered so that those belong to the same group are next to each other.
+The training vectors are aslo transformed to match the re-ordered features.\\
+
+The resulting weight matrix recoved is shown partically as below. The accuracy of the prediction is 93\%. The sparsity of the matrix is 52\% and the matrix is group-wise sparse.\\
+
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=\linewidth]{m4_img}
+  \caption{Part of the Weight matrix computed from 200 articles from 3 topics. Each column is one topic class. Each row is a feature/word.}
+\end{figure}%
 

### 2014-12-19 highdim-paper/paper.tex
added the missing image

@@
        Output these indices to a new group\\
-       Mark all cell in these columns in the matrix Z to be 0.\\
+       Mark all cells in these columns in the matrix Z to be 0.\\
   }

### 2014-12-19 highdim-paper/paper.tex
Doc updated

--- 2014-12-19 highdim-paper/paper.tex
@@
 \section{Introduction}
-We motivate our project by considering the text classification problem: 
-can we accurately classify text documents by topic. With the rapid growth 
+Our motivation for this project comes from text classification problem: 
+can we accurately classify text documents by topics. With the rapid growth 
 of online information, text categorization has become one of the key techniques 
@@
 Given the co-occurence matrix $Z$, a simple greedy algorithm below is used to generates groups for the features.
+The algorithm generates non-overlapping groups.
+To generate overlapping groups, skip step 3.
 
@@
   \For{$i \gets 0, \ldots, rows(Z) $}{
-	   Get the indices of the N largest columns from row i\\
-       Output these indices to a new group\\
-       Mark all cell in these columns in the matrix Z to be 0.\\
+	   1) Get the indices of the N largest columns from row i\\
+       2) Output these indices to a new group\\
+       3) Mark all cells in these columns in the matrix Z to be 0.\\
   }
@@
 
-Groups created from this method are more meaning semantically and more granular.
+Groups created from this method are more meaningful semantically and more granular.
 Further granularty can be achieved by couting the frequency of two features in sentence level other than article level.\\

### 2014-12-19 submission/baseline.py
Added submission folder and copied all files to submit into it. Need to write README

@@ -1,0 +1,196 @@
+import numpy as np
+import sys
+from sklearn.utils.extmath import safe_sparse_dot
+import scipy.sparse
+
+LOWER = 1e-2
+UPPER = 1e9
+
+class ColumnData(object):
+    def __init__(self, X):
+        self._X = scipy.sparse.csc_matrix(X)
+    def get_row(self,row):
+        return self._X[row,:]
+    def get_column(self, col):
+        """Iterator over (row, val) tuples for nonzero values in column col"""
+        for ii in range(self._X.indptr[col], self._X.indptr[col + 1]):
+           yield (self._X.indices[ii],  self._X.data[ii])
+
+
+class BaselineGroupLasso(object):
+    def __init__(self, max_iter=50, tol=1e-3, 
+                 alpha=1e-4, beta=.5, sigma=.01, max_steps=30):
+        self.tol = tol
+        self.max_iter = max_iter
+        self.alpha = alpha
+        self.max_steps = max_steps
+        self.sigma = sigma
+        self.beta = beta
+
+    def fit(self, X, y):
+
+        n_samples, n_features = X.shape
+        n_classes = np.unique(y).shape[0]
+
+        nv = n_samples * n_classes
+        violation_max_old = float('inf')
+        violation_init = 0
+
+        ds = ColumnData(X)
+
+        self.coefs_ = np.zeros((n_features, n_classes))
+        A = np.ones((n_samples, n_classes))
+        error_weight = 1. / n_samples
+
+        inactive = set()
+        active_set = range(0, n_features)
+        active_size = len(active_set)
+        active_size_start = active_size
+        for n_iter in xrange(self.max_iter):
+            print "iter", n_iter + 1
+            violation_max = 0
+            violation_sum = 0
+
+            for j in active_set:
+                if j in inactive:
+                    continue
+                Gj, Lpp_max, loss_j = self._derivatives(
+                    A, ds, y, j, n_classes, error_weight)
+                Gj_norm = np.linalg.norm(Gj, 2)
+                Rj = np.linalg.norm(self.coefs_[j,:], 2)
+
+                if Rj == 0:
+                    Gj_norm -= self.alpha
+                    if Gj_norm > 0:
+                        violation = Gj_norm
+                    elif Gj_norm + violation_max_old / nv <= 0:
+                        # Shrink!
+                        if self.verbose >= 2:
+                            print "Shrink variable", j
+                            inactive.add(j)
+                            active_size -= 1
+                            continue
+                            #return 1
+                else:
[…]

### 2014-12-19 submission/newimplgroup_syn.py

@@ -1,0 +1,200 @@
+import numpy as np
+from sklearn.utils.extmath import safe_sparse_dot
+import scipy.sparse
+from sklearn.datasets import fetch_20newsgroups
+from sklearn.feature_extraction.text import TfidfVectorizer
+from time import time
+from lightning.classification import CDClassifier
+import random
+import sys
+
+class ColumnData(object):
+    def __init__(self, X):
+        self._X = scipy.sparse.csc_matrix(X)
+    def get_row(self,row):
+        return self._X[row,:]
+    def get_column(self, col):
+        """Iterator over (row, val) tuples for nonzero values in column col"""
+        for ii in range(self._X.indptr[col], self._X.indptr[col + 1]):
+           yield (self._X.indices[ii],  self._X.data[ii])
+
+def calculate_AW(ds, y, n_samples, n_classes,coefs_):
+    AW =  np.ones((n_samples, n_classes))
+    for i in xrange(n_samples):
+        for r in xrange(n_classes):
+            Xi=ds.get_row(i)
+            AW[i,r]-=safe_sparse_dot(Xi,coefs_[:,y[i]]-coefs_[:,r])
+    return AW
+
+def calculate_loss(ds, y, n_samples, n_features, n_classes,coefs_, lamb, groups):
+    AW = calculate_AW(ds,y, n_samples, n_classes,coefs_)
+    LOSS = 0
+    LAMBDA = lamb
+    for i in xrange(n_samples):
+        for r in xrange(n_classes):
+            if y[i] != r:
+                #print i,y[i],r
+                LOSS += max(AW[i,r],0) ** 2    
+    LOSS/=float(n_samples)
+    for group in groups:
+        for m in xrange(n_classes):
+            LOSS += np.linalg.norm(coefs_[group[0]:group[1],m], 2) * LAMBDA
+    return LOSS
+ 
+def _derivatives(n_classes, j, ds, y, AW, one_over_n, m):
+    Gj = np.zeros((n_classes))
+    hj = np.zeros((n_classes))
+    for r in xrange(n_classes):
+        for i, Xij in ds.get_column(j):
+            if y[i] != r and AW[i,r] > 0:
+                if y[i] == m:
+                    Gj[y[i]] -= AW[i,r] * Xij
+                    hj[y[i]] += Xij * Xij
+                if r == m:
+                    Gj[r] += AW[i,r] * Xij
[…]

### 2014-12-19 submission/ogroup.py

@@ -1,0 +1,277 @@
+import numpy as np
+import sys
+from sklearn.utils.extmath import safe_sparse_dot
+import scipy.sparse
+
+LOWER = 1e-2
+UPPER = 1e9
+
+class ColumnData(object):
+    def __init__(self, X):
+        self._X = scipy.sparse.csc_matrix(X)
+    def get_row(self,row):
+        return self._X[row,:]
+    def get_column(self, col):
+        """Iterator over (row, val) tuples for nonzero values in column col"""
+        for ii in range(self._X.indptr[col], self._X.indptr[col + 1]):
+           yield (self._X.indices[ii],  self._X.data[ii])
+
+
+class BaselineGroupLasso(object):
+    def __init__(self, max_iter=50, tol=1e-3, 
+                 alpha=1e-4, beta=.5, sigma=.01, max_steps=30):
+        self.tol = tol
+        self.max_iter = max_iter
+        self.alpha = alpha
+        self.max_steps = max_steps
+        self.sigma = sigma
+        self.beta = beta
+
+    def fit(self, X, y, groups):
+
+        n_samples, n_features = X.shape
+        n_classes = np.unique(y).shape[0]
+
+        nv = n_samples * n_classes
+        violation_max_old = float('inf')
+        violation_init = 0
+        violation = 0
+
+        ds = ColumnData(X)
+
+        self.coefs_ = np.zeros((n_features, n_classes))
+        A = np.ones((n_samples, n_classes))
+        error_weight = 1. / n_samples
+
+        inactive = set()
+        active_set = range(0, n_features)
+        active_size = len(active_set) * n_classes
+        active_size_start = active_size
+
+        for n_iter in xrange(self.max_iter):
+            print "iter", n_iter + 1
+            violation_max = 0
+            violation_sum = 0
+
+            for r in xrange(n_classes): 
+                for g_id, group in enumerate(groups):
+                    g_start = group[0]
+                    g_end = group[1]
+                    if (g_id, r) in inactive:
+                        continue
+
+                    Ggr = np.zeros((g_end - g_start))
+                
+            #for j in active_set:
+            #    if j in inactive:
+            #        continue
+                    Lpp_max =-1<<31 
+                    for j in xrange(g_start, g_end):
+                        Gjr, Hjr, loss_g = self._derivatives_feat(
+                            A, ds, y, j, r, n_classes, error_weight)
[…]

### 2014-12-19 submission/ogroup_test_3ng.py

@@ -1,0 +1,64 @@
+
+
+import scipy.sparse
+from sklearn.datasets import fetch_20newsgroups
+from sklearn.feature_extraction.text import TfidfVectorizer
+from time import time
+from lightning.classification import CDClassifier
+import baseline
+import ogroup
+
+
+import random
+import numpy as np
+from sklearn.utils.extmath import safe_sparse_dot
+
+import get_3ng_aug_data as ng
+
+np.set_printoptions(precision=4)
+
+Xnew, y_train, groups, dict_text = ng.get_data()
+
+X_train = Xnew
+y_train = y_train
+
+
+print "### BASELINE GROUP LASSO in pure python/numpy###"
+X = X_train
+y = y_train
+clf = ogroup.BaselineGroupLasso(max_iter=50, alpha=.01,  max_steps=50)
+clf.fit(X, y, groups)
+print "Acc:", clf.score(X, y)
+print (clf.coefs_)
+
+
+import heapq
+
+top_words =  30
+
+for m in xrange(clf.coefs_.shape[1]):
+	t = []
+	print 'Topic',m
+	for row in xrange(clf.coefs_.shape[0]):
+		if( clf.coefs_[row,m] >0):
+			t.append( dict_text[row])
+	for k in heapq.nlargest(top_words,t):
+		print k,
+	print
+ 
+
+print "### Equivalent Lightning Cython Implementation ###"
+light_clf = CDClassifier(penalty="l1/l2",
+                         loss="squared_hinge",
+                         multiclass=True,
+                         max_iter=clf.max_iter,
+                         alpha=1e-4, # clf.alpha,
+                         C=1.0 / X.shape[0],
+                         tol=clf.tol,
+                         permute=False,
+                         verbose=3,
+                         random_state=0).fit(X, y)
+print "Acc:", light_clf.score(X, y)
+print (light_clf.coef_.T)
+
+

### 2014-12-19 highdim-paper/paper.tex
added references bbl and bst to paper
added \ref to algorithm

@@
 
-Many choices are available for the regularizer $r$. In (ref ???), they use
+Many choices are available for the regularizer $r$. \cite{blondel2013block} uses
 the group lasso, where each row in $W$ is a group. The associated regularizer 
@@
 
-To minimize this multiclass classification group lasso objective, ??? use 
-coordiante descent, iteratively solving a sub-problem with respect to a 
-single group. Figure ? shows a general outline of algorithm that involves
+To minimize this multi-class classification group lasso objective, coordinate descent method could be used, which iteratively solve a sub-problem with respect to a 
+single group. Algorithm~\ref{fig:cooddes} shows a general outline of algorithm that involves
 computing the partial gradient with respect to the 
@@
 \begin{algorithm}
+\caption{coordinate descent among groups}
+\label{fig:cooddes}
  \For{$i \gets 1, \ldots, max\;iters $}{
@@
 % include your own bib file like this:
-%\bibliographystyle{acl}
-%\bibliography{acl2014}
-
-%\begin{thebibliography}{}
-%
-%\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
-%Alfred~V. Aho and Jeffrey~D. Ullman.
-%\newblock 1972.
-%\newblock {\em The Theory of Parsing, Translation and Compiling}, volume~1.
-%\newblock Prentice-{Hall}, Englewood Cliffs, NJ.
-%
-%\bibitem[\protect\citename{{American Psychological Association}}1983]{APA:83}
-%{American Psychological Association}.
-%\newblock 1983.
-%\newblock {\em Publications Manual}.
-%\newblock American Psychological Association, Washington, DC.
-%
-%\bibitem[\protect\citename{{Association for Computing Machinery}}1983]{ACM:83}
-%{Association for Computing Machinery}.
-%\newblock 1983.
-%\newblock {\em Computing Reviews}, 24(11):503--512.
-%
-%\bibitem[\protect\citename{Chandra \bgroup et al.\egroup }1981]{Chandra:81}
-%Ashok~K. Chandra, Dexter~C. Kozen, and Larry~J. Stockmeyer.
-%\newblock 1981.
-%\newblock Alternation.
-%\newblock {\em Journal of the Association for Computing Machinery},
-%  28(1):114--133.
-%
-%\bibitem[\protect\citename{Gusfield}1997]{Gusfield:97}
-%Dan Gusfield.
-%\newblock 1997.
-%\newblock {\em Algorithms on Strings, Trees and Sequences}.
-%\newblock Cambridge University Press, Cambridge, UK.
-%
-%\end{thebibliography}
+\bibliographystyle{acl}
+\bibliography{ref}
 

### 2014-12-19 highdim-paper/paper.tex
added one more reference for latent group lasso

@@
 
-??? develop a theoretical justification for the latent group lasso, as well
+\cite{obozinski2011group} developed a theoretical justification for the latent group lasso, as well
 as its equivalence to a regular group lasso in a higher dimensional space.
@@
 $w = \sum_{g \in \mathcal{G}} v^g$. 
-??? arrive at the following minimization
-problem 
+So now the minimization problem is
 $$ \min_{w, v^g} l(w) + \lambda \sum_{g \in \mathcal{G}} d_g \|v^g \|_2 $$
@@
 
-??? show that when the original problem is regression, 
+When the original problem is regression, 
 $w^Tx = \left(\sum_g v^g\right)^Tx = \hat{v}^T \hat{x}$ where 
@@
 the restrictions of each $g$ stacked on top of each other. $\hat{x}, \hat{v}$ 
-have dimension $\sum_{g \in \mathcal{G}} |g|$ 
+have dimension $\sum_{g \in \mathcal{G}} |g|$.
 In this formulation, the optimal $\hat{v}^*$ can be found using regular 

### 2014-12-19 submission/get_3ng_aug_data.py
Code clean up

@@ -12,13 +12,17 @@ from nltk import PorterStemmer
 def get_data():
 	stem = PorterStemmer().stem_word
 
+	categories=['alt.atheism', 'comp.graphics', 'misc.forsale']
+	print "Retrieving articles from categories :",categories
+
 	newsgroups_train = fetch_20newsgroups(
-		categories=['alt.atheism', 'comp.graphics', 'misc.forsale'],
+		categories=categories,
 		subset='train', remove=('headers', 'footers', 'quotes'))
 
 	newsgroups_train.data = newsgroups_train.data[0:200]
 	newsgroups_train.target = newsgroups_train.target[0:200]
 
+	print "Pre-processing ... "
 	f = open("stopwords")
 	lines = f.readlines()
 	stoplist = set([ line.strip() for line in lines])
@@ -49,15 +53,13 @@ def get_data():
 				if word not in infrequent_words}
 				for text in texts]
 
-	print len(texts)
+	print "Number of articles : ",len(texts)
 
 	vec = DictVectorizer(dtype=np.int32)
 	X_train = vec.fit_transform(texts)
 
 	trans = TfidfTransformer()
 	X_train = trans.fit_transform(X_train)
-
-	print X_train.shape
 
 	y_train = newsgroups_train.target
 
@@ -88,7 +90,7 @@ def get_data():
 			already_chosen.add(v)
 		return words
 
-
+	print "Calculating co-occurence matrix and transforming data ..."
 	XX = X_train_bin.T.dot(X_train_bin)
 	already_chosen = set()
 	groups = []

### 2014-12-19 submission/newimplgroup_syn.py

@@ -118,6 +118,8 @@ def score(X, y, coefs_):
 
 np.set_printoptions(precision=3)
 
+############## Generating synthetic data #############
+
 m_classes = 5
 m_features = 25
 m_groups = 5
@@ -126,9 +128,15 @@ multiple = 1.3
 m_samples = 150
 attemp = 0
 
+print "Generating synthetic data ..."
+print "# of classes  :", m_classes
+print "# of features :", m_features
+print "# of groups   :", m_groups
+print "# of samples  :", m_samples
+
 while 1:
     attemp +=1
-    print 'attemp', attemp
+    #print 'Attemp', attemp
     groups = []
     weights = np.zeros((m_features,m_classes))
     idx = 0
@@ -148,10 +156,11 @@ while 1:
     X = np.random.rand(m_samples,m_features)
     pred = safe_sparse_dot(X, weights)
     y_pred = np.argmax(pred, axis=1)
-    print 'unique classes',  np.unique(y_pred).shape[0]
+    #print 'Unique classes',  np.unique(y_pred).shape[0]
     if np.unique(y_pred).shape[0] == m_classes:
         break
 
+print "================= Data Summary  ======================"
 print 'weights', weights
 print 'groups', groups
 print 'y_pred', y_pred
@@ -162,7 +171,8 @@ sys.stdin.readline()
 X_train = X
 y_train = y_pred
 
-
+print "========= Group Lasso (Block-wise sparsity)========="
+print "** Slow version **"
 X = X_train
 y = y_train
 n_features = X.shape[1]
@@ -174,13 +184,13 @@ coefs_ = np.zeros((n_features, n_classes))
 
 fit( ds, y, one_over_n, n_samples, n_features, n_classes,coefs_,groups)
 s =  score (X,y,coefs_)
-print "score = ", s
+print "=====> Accuracy : ", s
 
 print '======================================================'
 
 clf_max_iter=300
 clf_tol = 1e-3
-print "### Equivalent Lightning Cython Implementation ###"
+print "========= Lightning Cython Implementation (Row-wise sparsity)========="
 light_clf = CDClassifier(penalty="l1/l2",
                          loss="squared_hinge",
                          multiclass=True,
@@ -191,7 +201,7 @@ light_clf = CDClassifier(penalty="l1/l2",
                          permute=False,
                          verbose=3,
                          random_state=0).fit(X, y)
-print "Acc:", light_clf.score(X, y)
[…]

### 2014-12-19 submission/ogroup_test_3ng.py

@@ -23,12 +23,13 @@ X_train = Xnew
 y_train = y_train
 
 
-print "### BASELINE GROUP LASSO in pure python/numpy###"
+print "==== Block-wise group lasso ===="
 X = X_train
 y = y_train
 clf = ogroup.BaselineGroupLasso(max_iter=50, alpha=.01,  max_steps=50)
 clf.fit(X, y, groups)
-print "Acc:", clf.score(X, y)
+print "=========>> Accuracy :", clf.score(X, y)
+print "Weight Matrix:"
 print (clf.coefs_)
 
 
@@ -36,6 +37,7 @@ import heapq
 
 top_words =  30
 
+print "==== Keywords ==== "
 for m in xrange(clf.coefs_.shape[1]):
 	t = []
 	print 'Topic',m
@@ -47,7 +49,7 @@ for m in xrange(clf.coefs_.shape[1]):
 	print
  
 
-print "### Equivalent Lightning Cython Implementation ###"
+print "==== Lightning Cython Implementation (Row-wise sparsity) ====="
 light_clf = CDClassifier(penalty="l1/l2",
                          loss="squared_hinge",
                          multiclass=True,
@@ -58,7 +60,8 @@ light_clf = CDClassifier(penalty="l1/l2",
                          permute=False,
                          verbose=3,
                          random_state=0).fit(X, y)
-print "Acc:", light_clf.score(X, y)
+print "==========>> Accuracy :", light_clf.score(X, y)
+print "Weight Matrix:"
 print (light_clf.coef_.T)
 
 

### 2014-12-19 highdim-paper/paper.tex

@@
 confidence is selected as the label. This approach has the disadvantage of
-having to train $k$ different models.
+having to train $k$ different models.\\
 
@@
 to features as elements in the instance data $x$. A feature in $x$ is
-associated with $k$ weights in $W$, one for each class.
+associated with $k$ weights in $W$, one for each class.\\
 
@@
 yields a fast-evaluating decision function, i.e. most features are 
-ignored at test time.
+ignored at test time.\\
 
 To minimize this multi-class classification group lasso objective, coordinate descent method could be used, which iteratively solve a sub-problem with respect to a 
-single group. Algorithm~\ref{fig:cooddes} shows a general outline of algorithm that involves
+single group. Algorithm~\ref{alg:cooddes} shows a general outline of algorithm that involves
 computing the partial gradient with respect to the 
@@
 \caption{coordinate descent among groups}
-\label{fig:cooddes}
+\label{alg:cooddes}
  \For{$i \gets 1, \ldots, max\;iters $}{
@@
 where one word could reasonably be added to several groups. The overlapping or
-latent group lasso was introduced to handled such cases.
+latent group lasso was introduced to handled such cases.\\
 
@@
 Finally, define $\operatorname{supp}(v)$ to be the support of $v$, i.e.
-the indices of the non-zero elements in $v$.
+the indices of the non-zero elements in $v$.\\
 
@@
 $$\mathrm{s.t.}\;\;\; w = \sum_g v^g$$ 
-
 When the original problem is regression, 
@@
 The $\lambda > 0$ is a parameter controls the trade-off between the hinge loss and the L2-norm regulization.
-\\
 
@@
 For each cluster we formed a feature group by taking the complete set of 
-non-zero features for each document in the group.
+non-zero features for each document in the group.\\
 
@@
 
-Given the co-occurence matrix $Z$, a simple greedy algorithm below is used to generates groups for the features.
+Given the co-occurence matrix $Z$, algorithm~\ref{alg:groupgen}  is used to generates groups for the features.
 The algorithm generates non-overlapping groups.
@@
 \begin{algorithm}
+\caption{group generation}
+\label{alg:groupgen}
   \For{$i \gets 0, \ldots, rows(Z) $}{
@@
 Groups created from this method are more meaningful semantically and more granular.
-Further granularty can be achieved by couting the frequency of two features in sentence level other than article level.\\
+Further granularty can be achieved by couting the frequency of two features in sentence level other than article level.
 

### 2014-12-19 highdim-paper/paper.tex
Small paper edits plus conclusion

@@
 
-\title{High-Dim Project}
+\title{Multi-class Overlapping Group Lasso Classification }
 
@@
 original problem is transformed into $k$ binary classification problems, i.e.
-$1$--vs.--all classification and positive prediction with the highest 
+$1$--vs.--all classification and the positive prediction with the highest 
 confidence is selected as the label. This approach has the disadvantage of
@@
 to features as elements in the instance data $x$. A feature in $x$ is
-associated with $k$ weights in $W$, one for each class.\\
+associated with $k$ weights in the row $W_{j:}$, one for each class.\\
 
@@
 
-Efficient computation of this objective is possible by storing current 
+\cite{blondel2013block} chose 
+$\mathcal{L}_j = \max_c l^{\prime\prime}(W)_{jc}$, the max element of the
+Hessian of the loss with respect to the $j$-th row. $\alpha$ is identified
+via line search.
+
+Efficient computation of this objective is possible by storing the current 
 loss for each data point. Let $A$ be an $n\times k$ matrix where the 
@@
 $$ \min_{W \in R^{d x m}} F(W) = $$
-$$\frac{1}{n} \sum_{i=1}^{n} \sum_{r \neq y_i } \max(1 - ( W_{:y_i}^T \cdot x_i - W_{:r}^T \cdot x_i) , 0 )^2 $$
+$$\frac{1}{n} \sum_{i=1}^{n} \sum_{r \neq y_i } \max(1 - ( W_{:y_i}^T  x_i - W_{:r}^T x_i) , 0 )^2 $$
 $$ + \lambda \sum_{g \in \mathcal{G}} \sum_{r=1}^{d} \| W_{g,r} \|_2$$ \\
 
-The first term is the multiclass squared hinge loss function.
-We want the dot product of an instance and its feature vector to be as large as possible, and the dot product of this instance and the rest feature vectors to be as small as possible.
-And as long as their difference is greater then a margin ($1$ in this case), we won't penalize it.
-In the second term, $W_{g,r}$ means a block of weights in group $g$ and class $m$.
-The L2-norm regulization is computed and sum up for each block.
-The $\lambda > 0$ is a parameter controls the trade-off between the hinge loss and the L2-norm regulization.
+The first term is the multiclass squared hinge loss function. We want the dot 
+product of an instance and its gold class weight vector to be as large as 
+possible, while the dot product with the weight vectors for alternate classes
+to be as small as possible. And as long as their difference is greater then 
+a margin ($1$ in this case), we won't penalize it.
+ In the second term, $W_{g,r}$ means a block of weights in group $g$ and 
+ class $m$. The L2-norm regulization is computed and summed up for each block.
+The $\lambda > 0$ is a parameter controls the trade-off between the hinge loss
+ and the L2-norm regulization.
 
@@
 
-Given the co-occurence matrix $Z$, algorithm~\ref{alg:groupgen}  is used to generates groups for the features.
-The algorithm generates non-overlapping groups.
-To generate overlapping groups, skip step 3.
+Given the co-occurence matrix $Z$, algorithm~\ref{alg:groupgen}  is used to
+ generate groups of the features. The algorithm generates 
+ non-overlapping groups. To generate overlapping groups, skip step 3.
 
@@
 
-Groups created from this method are more meaningful semantically and more granular.
+Groups created from this method are more meaningful semantically and more 
+granular. 
 Further granularty can be achieved by couting the frequency of two features in sentence level other than article level.
@@
 \section{Conclusion}
+In this paper, we have presented an extension to the multi-class group lasso,
+taking advantage of overlapping groups. In addition we experimented with 
+an automatic covariate group generation method using the co occurrence matrix.
+Our approach shows promising results, but we still need to improve the 
+scalability of this algorithm.
+
 % include your own bib file like this:
